A thesis draft

### 2018-11-30 res/sections/08-Background.tex
Fix typo

\paragraph{Data Repositories}
Data repositories can be seen as a sort of databases, holding information about
the VNF definitions, the VNF instances with the respective lifecycle status, a
list of the Network Services defined and the resources rispectively available
and occupied of the NFVI.

>>>>

\paragraph{Data Repositories}
Data repositories can be seen as a sort of databases, holding information about
the VNF definitions, the VNF instances with the respective lifecycle status, a
list of the Network Services defined and the resources respectively available
and occupied of the NFVI.
